Alexis Roche

### 2021-01-07 cv/cv.tex
update cv

\bighead{HEAD OF COMPUTER VISION \& ARTIFICIAL INTELLIGENCE}{Didimo, Porto, Portugal}{2019--present}
\nopagebreak
\begin{itemize}
\item Developing computer vision and machine learning algorithms for high-fidelity 3D avatars.
\end{itemize}
\ \\

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Programming:}
\ \\ 
\ \\
\ \\ 
\ \\
\ \\ 
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} C/C++ \\
{\tiny$\bullet$} Python (numpy, scipy, pylab, skimage, opencv, sklearn, TensorFlow, Keras, ...)\\
{\tiny$\bullet$} C/Python integration via Cython\\
{\tiny$\bullet$} Matlab\\
{\tiny$\bullet$} R \\
{\tiny$\bullet$} Version control software: Git, SVN, Perforce. \\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6147 citations, h-index: 32, i10-index: 62 (October 2020).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}

>>>>

\bighead{HEAD OF COMPUTER VISION \& ARTIFICIAL INTELLIGENCE}{Didimo, Porto, Portugal}{2019--present}
\nopagebreak
\begin{itemize}
\item Developing computer vision and machine learning algorithms for reconstruction of high-fidelity digital humans from photos.
\end{itemize}
\ \\

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Programming:}
\ \\ 
\ \\
\ \\ 
\ \\
\ \\ 
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Programming languages: C, Python, Matlab, R. \\
{\tiny$\bullet$} Python packages: numpy, scipy, pylab, skimage, opencv, sklearn, pytorch, TensorFlow, keras.\\
{\tiny$\bullet$} C/Python integration via cython.\\
{\tiny$\bullet$} Version control software: git, svn, perforce. \\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6225 citations, h-index: 32, i10-index: 63 (December 2020).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}
